Illustrating Model Properties

### 2024-05-17 model.qmd
start with midext prevalence plot

>>>>

## Portion of Midline Extension

Since we model the tumor's midline extension as a random variable we can predict its portion among early or late T-category patients and compare it with the observed prevalence in the data.

```{python}
#| label: fig-model-prevalence-midext
#| fig-cap: "Comparing the predicted (histograms) and observed (lines depicting beta posteriors) prevalence of midline extension for early (blue) and late (orange) T-category."
pass
```
